### 2014-10-03 tex/definitions.tex
Renamed location mutual exclusion to detemrnism
Macro'd and renamed all the relations and state designations--first pass

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states. Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_\varsigma$. Each of these use a separate relation for initialization: $\rightarrow_I$ for initialization the lazy transition relation and $\rightarrow_S$ for initialization the summary transition relation. All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}

@@

\begin{definition}
A heap, $(\cfgnt{L}\ \cfgnt{R})$, is \textbf{location mutual exclusive} if and only if 
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi_\alpha\ \cfgnt{l}_\alpha),(\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}(r)\ (\\
\ \ \ \ \cfgnt{l}_\alpha \neq \cfgnt{l}_\beta \Rightarrow \phi_\alpha \wedge \phi_\beta = \cfgt{false}))
\end{array}
\]
\end{definition}

>>>>

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states. Two important state transition relations are \textbf{GSE} $\rgse$ and \textbf{symbolic} $\rsym$. Each of these use a separate relation for initialization: $\rinit$ for GSE and $\rsum$ for symbolic. All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}

@@

\begin{definition}
A heap, $(\cfgnt{L}\ \cfgnt{R})$, is \textbf{deterministic} if and only if 
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
\end{array}
\]
\end{definition}
